### 2014-08-13 paper/paper.Rmd
topics
topics done

>>>>

### Teachers, computers, and libraries at school matter

### Gender gap in math is not universal but the reading gap is

### School start age affects performance

### Time spent out of school studying is important, but only up to a point

### More TVs yield higher math scores in the developing world, but lower in the developed countries

### Parents matter

### The weird and wacky republic of Albania
